Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/overview.tex
wordsmithing

In \ref{fig:qs-staged} we show a staged version of \texttt{qs}, called
\texttt{qss}, where first-stage code is colored red, and second-stage blue. In
\texttt{qss}, we regard the input list as arriving in the first stage
(with type $\curr\mathrm{list}$, a list ``now''), the input rank as arriving in
the second stage (with type $\fut\rmint$, an integer in the ``future''), and the
result as being produced in the second stage (with type $\fut\rmint$).

>>>>

In \ref{fig:qs-staged} we show a staged version of \texttt{qs}, called
\texttt{qss}, where first-stage code is colored red, and second-stage blue. In
\texttt{qss}, we regard the input list \texttt{l} as arriving in the first stage
(with type $\curr\mathrm{list}$, a list ``now''), the input rank \texttt{k} as
arriving in the second stage (with type $\fut\rmint$, an integer in the
``future''), and the result as being produced in the second stage (with type
$\fut\rmint$).
